Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2021-11-30 proposalPres.tex
Updated proposalPres.tex
Adjusted slides to fit new figures
Edited font sizes to match

\usepackage{pgfgantt}
\usepackage{todonotes}
\usepackage{media9}
\usepackage{fontawesome5}
\usepackage{subfigure}
\usepackage{booktabs,array}
\usepackage{tabulary}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{arydshln}

@@

\begin{frame}{Problem Statement}
  \begin{block}{Problem Statement}
      Model different subsystems for an autonomous vehicle (Lexus RX450H platform is considered in this project), which are
      \begin{itemize}
          \item Steering
          \item Acceleration
          \item Brake
          \item Shift
          \item Speed
          \item Speed control
        \end{itemize} 
        using input-output raw data available offline

          \begin{figure}
			\centering
			\begin{minipage}[t]{0.4\textwidth}
				%\centering

				\includegraphics[height=1.5cm]{figs/img/picturesVisitToAStuff/visitors1-20211007}
				\caption{AutonomouStuff Vehicle Fleet\textsuperscript{a}}

			\end{minipage}
			\end{figure}
  \end{block}

@@

\begin{frame}{System Requirements}
	\tiny  
  \begin{block}{Specifications}
    Proposed vehicle subsystem models are expected to fulfill requirements listed below:
\begin{itemize}
    \item Resulting plant model will consist of reasonably accurate subsystem models
    \item Subsystems can be used to create a HIL testbench
    \item Steering model can handle very small changes in steering angles
    \begin{itemize}
		\tiny    		
    		\item smooth out any non-linear discontinuities that would normally be measured by the steering motor, especially for small changes in the steering angle, depicted in \autoref{fig:nonlinGraph}.
    \end{itemize}
\end{itemize}
\begin{figure}[h]
	\tiny    
    \centering
    \captionsetup{justification=centering, margin=3cm}
    \includegraphics[width=1in]{figs/inkscape/nonlinearBehavior}
    \caption{Steering Non-linear Behavior}
    \label{fig:nonlinGraph}
\end{figure}
  \end{block}
\end{frame}

@@

\begin{frame}{By-Wire Acceleration System Transfer Function}
	\begin{block}{Fourth-Order ARX Model}
		\begin{equation}
			A(z)y(t) = B_1(z)u_1(t) + B_2(z)u_2(t) + e(t)
		\end{equation}
		%
		where na = 4, nb = 4, nk = 0, and, 
		%
		\begin{equation}
			A(z) = 1 - 1.018z^{-1} - 0.002901z^{-2} + 0.4631z^{-3} - 0.2038z^{-4}
		\end{equation}
		\begin{equation}
			B_1(z) = -0.0207 - 0.01912z^{-1} - 0.02159z^{-2} - 0.03307z^{-3}
		\end{equation}
		\begin{equation}
			B_2(z) = 0.02017 + 0.01833z^{-1} + 0.09461z^{-2} + 0.05683z^{-3}
		\end{equation}
	\end{block}
\end{frame}

>>>>

\usepackage{pgfgantt}
\usepackage{todonotes}
\usepackage{media9}
\usepackage{fontawesome5}
\usepackage{subfigure}
\usepackage{booktabs,array}
\usepackage{tabulary}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{arydshln}
\usepackage{multicol}

@@

\begin{frame}{Problem Statement}
  \begin{block}{Problem Statement}
	\begin{minipage}[t]{0.62\linewidth}      
      Model different subsystems for an autonomous vehicle (Lexus RX450H platform is considered in this project), which are
	  \begin{multicols}{2}      
      \begin{itemize}
          \item Steering
          \item Acceleration
          \item Brake
          \item Shift
          \item Speed
          \item Speed control
        \end{itemize} 
        \end{multicols}
        using input-output raw data available offline
    \end{minipage}
    \begin{minipage}[t]{0.34\textwidth}  
        \begin{figure}
			\centering
			\captionsetup{justification=centering, margin=0.5cm, font=tiny}
			\includegraphics[width=4cm]{figs/img/picturesVisitToAStuff/visitors1-20211007}
			\caption{AutonomouStuff Lexus RX450H Vehicle}
		\end{figure}
	\end{minipage}
  \end{block}

@@

\begin{frame}{System Requirements}
\begin{block}{Specifications}
	\begin{minipage}[t]{0.62\linewidth}    
    Proposed vehicle subsystem models are expected to fulfill requirements listed below:
	\begin{itemize}
    		\item Resulting plant model will consist of reasonably accurate subsystem models
    		\item Subsystems can be used to create a HIL testbench
    		\item Steering model can handle very small changes in steering angles
    \begin{itemize}
		\item smooth out any non-linear discontinuities that would normally be measured by the steering motor, especially for small changes in the steering angle, depicted in \autoref{fig:nonlinGraph}.
    \end{itemize}
	\end{itemize}
	\end{minipage}
	\begin{minipage}[t]{0.34\linewidth}
	\begin{figure}[h]
		\centering
    		\captionsetup{justification=centering, margin=0.5cm}
    		\includegraphics[width=1.5in]{figs/inkscape/nonlinearBehavior}
    		\caption{Steering Non-linear Behavior}
    		\label{fig:nonlinGraph}
	\end{figure}
	\end{minipage}
\end{block}
\end{frame}

@@

\begin{frame}{By-Wire Acceleration System Transfer Function}
	\begin{block}{Fourth-Order ARX Model}
		\begin{equation}
			A(z)y(t) = B_1(z)u_1(t) + B_2(z)u_2(t) + e(t)
		\end{equation}
		%
		\centering where na = 4, nb = 4, nk = 0, and, 
		%
		\begin{equation}
			A(z) = 1 - 1.018z^{-1} - 0.002901z^{-2} + 0.4631z^{-3} - 0.2038z^{-4}
		\end{equation}
		\begin{equation}
			B_1(z) = -0.0207 - 0.01912z^{-1} - 0.02159z^{-2} - 0.03307z^{-3}
		\end{equation}
		\begin{equation}
			B_2(z) = 0.02017 + 0.01833z^{-1} + 0.09461z^{-2} + 0.05683z^{-3}
		\end{equation}
	\end{block}
\end{frame}
